A Container-Based Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-10-15 draft.tex
Proposed method intro

Later approaches used microservices \cite{khalloof2018generic} and 
provided the automation of the whole workflow\cite{salza2019speed}, 
achieving speed-up by creating an abstraction layer over the 
evolutionary algorithm services.
%, and also automation of the whole workflow. 
This research bumped into some problems, since speed-up is limited, mainly due to the
non-automatic scaling of services and the presence of a single
master, which is the one that runs the evolutionary
algorithm. However, this master-worker architecture can be turned
around with other kinds of evolutionary architectures, such
as pool-based systems
\cite{valenzuela2015implementing,merelo2012sofea,sofea:cec2012} that were 
a better match to the inherently heterogeneous nature of cloud-based
architectures. Pool-based systems are closer to serverless systems
\cite{malawski2017serverless}, as they pull populations from the pool and run
whole algorithms, instead of just doing the evaluation. The pool 
is a shared data storage for results, and can be accessed in an
asynchronous way, which suits better the nature of cloud-native systems.

@@

In this section, we present the design
and a container-based implementation of the model we propose for the execution
of multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mentioned earlier; our intention is to steer
clear of a direct translation of ``classical'' GA architectures to the
cloud and design from the ground up a cloud-native method. As a first step, we describe the general
architecture, and then  every component in detail.

The most elemental data structure used throughout the system is the population; and at a higher
level, we can view the system as a continuous stream of populations
flowing from one process to the other. By ``continuous stream,'' we mean that ideally,
everything must happen asynchronously without components needing to wait for
others. In this kind of system, this streaming functionality is normally
implemented by using a message queue system. For instance, if one process needs
to communicate a population to another, it must pack the population into
a message, and then send the message 
to the queuing system without waiting for a response; this
means that after the process pushes the message, it continues its execution
without waiting for a result. On the other end, the recipient subscribes to the
message queue by defining an event handler method that is going to be triggered when a
message is pushed to it. The two components at each end of the queue are
Producers that push messages to the queue and Consumers that pull them. This
pattern is an essential component of a reactive architecture and makes
it highly scalable; one of the reasons for this is the use of functions
that have no secondary effects or access global storage, that is,
stateless functions. These functions do not need to read, keep, or modify data outside of the method. If
Consumers are implemented using stateless functions, and thus, there is no difference
between having one or many copies of the same function pulling work from the queue all at the
same time, because no side effects, including unwanted resource
locking problems,  are going to result from this concurrency.
% This is important and we should probably mention that in the
% introduction - JJ 
Based on these general principles, we next define the proposed model.

>>>>

Later approaches used microservices \cite{khalloof2018generic} and 
provided the automation of the whole workflow\cite{salza2019speed}, 
achieving speed-up by creating an abstraction layer over the 
evolutionary algorithm services.
%, and also automation of the whole workflow. 
This research bumped into some problems, since speed-up is limited, mainly due to the
non-automatic scaling of services and the presence of a single
master, which is the one that runs the evolutionary
algorithm. However, this master-worker architecture can be turned
around with other kinds of evolutionary architectures, such
as pool-based systems
\cite{valenzuela2015implementing,merelo2012sofea,sofea:cec2012} that were 
a better match to the inherently heterogeneous nature of cloud-based
architectures. Pool-based systems are closer to serverless systems
\cite{malawski2017serverless}, as they pull populations from the pool and run
whole algorithms, instead of just doing the evaluation. The pool 
is a shared data storage for results and can be accessed in an
asynchronous way, which suits better the nature of cloud-native systems.

@@

In this section, we present the design
and a container-based implementation of the model we propose to execute
multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mentioned earlier; we intend to steer
clear of a direct translation of ``classical'' GA architectures to the
cloud and design from the ground up a cloud-native method. As a first step, we describe the general
architecture and then every component in detail.

The most basic data structure used throughout the system is the population, and at a higher
level, we can view the system as a continuous stream of populations
flowing from one process to the other. By ``continuous stream,'' we mean that ideally,
everything must happen asynchronously without components needing to wait for
others. In this kind of system, this streaming functionality is normally
implemented by using a message queue system. For instance, if one process needs
to communicate a population to another, it must pack the population into
a message and then send the message 
to the queuing system without waiting for a response; this
means that after the process pushes the message, it continues its execution
without waiting for a result. On the other end, the recipient subscribes to the
message queue by defining an event handler method that will be triggered when a
message is pushed to it. At each end of the queue, the two components are 
Producers that push messages to the queue and Consumers that pull them. This
pattern is an essential component of a reactive architecture and makes
it highly scalable; one reason for this is the use of functions
with no secondary effects, that is,
stateless functions. These functions do not need to read, keep, or modify data outside of the method. If
Consumers are implemented using stateless functions, there is no difference
between having one or many copies of the same function pulling work from the queue 
simultaneously, because there are no side effects, including unwanted resource
locking problems resulting from this concurrency.
% This is important and we should probably mention that in the
% introduction - JJ 
Based on these general principles, we next define the proposed model.
